\Large {\bf Flow-guided Analysis of System-level Post-silicon Traces Under Limited Observability}

### 2015-09-07 paper.tex

>>>>

Post-silicon validation makes use of pre-production silicon
integrated circuit (IC) to ensure that the fabricated system
works as desired under actual operating conditions with real
software.  Since the silicon executes at target clock speed,
post-silicon executions are billions of times faster than
RTL simulations, and even provide speed-up of several orders
of magnitude over other pre-silicon platforms (\eg, FPGA,
system-level emulation, etc.).  This makes it possible to
explore deep design states which cannot be exercised in
pre-silicon, and identify errors missed during pre-silicon
validation and debug.  Post-silicon validation is a critical
component of the design validation life-cycle for modern
microprocessors and SoC designs.  Unfortunately, it is also
a highly complex component, performed under aggressive
schedules and accounting for more than $50\%$ of the overall
design validation cost.  Consequently, it is crucial to
develop techniques for streamlining and automating
post-silicon validation activities.

A central component of post-silicon validation is to
correlate trace from silicon execution with the intended
behavior of the sysem.  As an example, consider a silicon
execution of a smartphone executing a post-silicon use case
where the end-user browses the Web while listening to music
and sending and receiving occasional text messages.  Such a
an execution trace would involve activities from the CPU,
audio controller, display controller, wireless radio
antenna, etc., reflecting the interleaved execution of
several communication protocols.  On the other hand, due to
observability limitations, only a small small number of
participating signals can be actually traced during silicon
execution.  Furthermore, due to electrical perturbations,
silicon data can be noisy, lossy, and ambiguous.
Consequently, it is non-trivial to identify all
participating protocols and pinpoint the ``right''
interleaving that results in an observed trace.

In this paper, we consider the problem of reconstructing
protocol-level behavior from silicon traces in SoC designs.
